experiment 1

### 2021-10-26 experiments/experiment 1/experiment-1.Rmd
Move some more calculations into parallel

rm(list = ls())

@@

Bring in various stable state datasets
```{r eval = TRUE}
## sim length 80'000, 20 x 20 factorial, reference maximum diversity

var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
  mutate(sim_length = 80000)

stab_data1 <- var_expt1 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data1 <- unnest(stab_data1, cols = c(stability_measures))
saveRDS(stab_data1, here("experiments/experiment 1/data/stab_data_80000.RDS"))

## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data2 <- var_expt2 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data3 <- var_expt3 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
  mutate(sim_length = 300000)
stab_data4 <- var_expt4 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
var_expt5 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data5 <- var_expt5 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```

>>>>

# rm(list = ls())

@@

Bring in various stable state datasets
```{r eval = TRUE}
cluster <- multidplyr::new_cluster(7)
multidplyr::cluster_library(cluster, c("microxanoxBeta", "dplyr"))

## sim length 80'000, 20 x 20 factorial, reference maximum diversity
readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
  mutate(sim_length = 80000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))

## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
# var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
#   mutate(sim_length = 1000000)
# # stab_data2 <- var_expt2 %>%
# #   group_by(CB_var_gmax_s, CB_var_h_s,
# #            SB_var_gmax_s, SB_var_h_s,
# #            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
# #   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data2 <- var_expt2 %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res)))
# stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
# saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
# var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
#   mutate(sim_length = 1000000)
# stab_data3 <- var_expt3 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
# saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
# var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
#   mutate(sim_length = 300000)
# stab_data4 <- var_expt4 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
# saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
  mutate(sim_length = 300000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
# var_expt5 <- readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
#   mutate(sim_length = 1000000)
# stab_data5 <- var_expt5 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
# saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```
